Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/RelatedWork.tex
stuff
Pass through larval RelatedWork

Formal verification of hardware-oriented cache coherence protocols, is mainly
done using model checking. In practice, explicit state model checking tools like
Murphi \cite{murphi} or TLC \cite{tlc} are only able to handle small and
simplified systems, \eg{} a single-level cache hierarchy with three CPUs, two
addresses, and one bit of data. Symbolic model checking techniques have fared
slightly better; McMillan \etal{} have verified a 2-level MSI protocol based on
Gigamax distributed multiprocessor using SMV.  Optimizations on these techniques
(\eg{} partial order reduction \cite{part}, symmetry reduction \cite{sym1,
  sym2}, compositional reasoning \cite{somethink}, \etc{} scale the approach
further, but they are still unable to handle realistic hierarchical protocols.

Theorem provers have also been used in verifying cache coherence protocols. The
FLASH coherence protocol \cite{flash} was verified using Aggregation of
Distributed transactions \cite{park}, where several state transitions accessing
localized state intuitively correspond to an aggregate atomic transition
accessing all global state. A proof of a mapping between the local transitions
and the agreggate one must be provided. Once this is done, a model checker can
be used to verify the aggregate model is correct. However, We believe that the
verification challenge here is precisely the proof of such a mapping which was
not discussed.

>>>>

Formal verification of hardware-oriented cache coherence protocols is mainly
done using model checking. In practice, explicit-state model checking tools like
Murphi \cite{murphi} or TLC \cite{tlc} are only able to handle small and
simplified systems, \eg{} a single-level cache hierarchy with three CPUs, two
addresses, and one bit of data. Symbolic model checking techniques have fared
slightly better; McMillan \etal{} have verified a 2-level MSI protocol based on
the Gigamax distributed multiprocessor using SMV.  Optimizations on these techniques
(\eg{} partial order reduction \cite{part}, symmetry reduction \cite{sym1,
  sym2}, compositional reasoning \cite{somethink}, \etc{}) scale the approach
further, but they are still unable to handle realistic hierarchical protocols.

Theorem provers have also been used in verifying cache coherence protocols. The
FLASH coherence protocol \cite{flash} was verified using Aggregation of
Distributed \adamc{why are these words capitalized?} transactions \cite{park}, where several state transitions accessing
localized state intuitively correspond to an aggregate atomic transition
accessing all global state. A proof of a mapping between the local transitions
and the agreggate one must be provided, at which point a model checker can
be used to verify that the aggregate model is correct. However, we believe that the
verification challenge here is precisely the proof of such a mapping, which was
not discussed.

Other approaches involve correct-by-construction
